Using reference models in feature selection problems \vspace{.1in}

### 2019-11-25 paper/ref_approach.tex
slightly bigger font size for tables
update graphics

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|lr|lr}
%  \hline
M & projpred & Freq \% & steplm & Freq \%  \\ 
  \hline
1 & abdom, weight & 39 & abdom, age, forearm, height, hip, neck, thigh, wrist & 4 \\
2 & abdom, wrist & 10 & abdom, age, chest, forearm, height, neck, thigh, wrist & 4 \\
3 & abdom, height & 10 & abdom, forearm, height, neck, wrist & 2 \\
4 & abdom, height, wrist & 9 & abdom, forearm, neck, weight, wrist & 2 \\
5 & abdom, weight, wrist & 8 & abdom, age, height, hip, thigh, wrist & 2 \\
6 & abdom, chest, height, wrist & 2 & abdom, age, height, hip, neck, thigh, wrist & 2 \\
7 & abdom, biceps, weight, wrist & 2 & abdom, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
8 & abdom, height, weight, wrist & 2 & abdom, age, biceps, chest, height, neck, wrist & 2 \\
9 & abdom, age, wrist & 2 & abdom, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
10 & abdom, age, height, neck, thigh, wrist & 2 & abdom, age, ankle, biceps, weight, wrist & 2 \\
%   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
  \hline
original & projpred & 4.35 & 4.47 & 2 &   \\
& steplm & 4.38 & 4.47 & 7 &  \\
\hline
+ noisy features & projpred & 4.58 & 4.54 & 2 & 0  \\
& steplm & 5.89 & 5.43 & 19 & 13 \\
%   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two
  rows) and with extra noisy features (last two rows) estimated with
  10-fold cross-validation. Abbreviations: Full = full model; Selected =
  selected submodel; \# Selected = total number of features selected;
  \# Selected noisy = number of extra noisy features selected.}
\label{tab:model_performances}
\end{table}

@@

When the variable selection is repeated with different simulated data
sets, there is some variability in which variables are selected. We
measure the stability of variable selection by computing the entropy
of observed distribution over different models. The smallest entropy
would be obtained if the approach selectes always the same set of
variables, and the largest entropy would be observed if the approach
would always select different set of variables.
Figure \ref{fig:entropy} reports the entropy scores for the different
methods compared. Lower entropy corresponds to a more stable
selection. Highly correlated predictive features may happen to be
alternately selected, making the measure of the stability of the
selection a non-trivial task. Entropy can not distinguish the interchangeability 
due to correlation from instability, thus such a measure should be 
consider as relative indicator and not as an absolute measure of stability.
\hl{TODO: The above sentence should be clearer now}
The use of a reference model
improves slightly the stability of steplm in feature selection. The
projection predictive approach results to be far more stable than all
other approaches. This is likely due to projpred being based on better
decision theoretical formulation which 1) takes into account the full
predictive distribution and not just point estimate and 2) projects
the reference model posterior to the submodel instead of using a
simple refit of submodels.

>>>>

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{l|lr|lr}
%  \hline
M & projpred & Freq \% & steplm & Freq \%  \\ 
  \hline
1 & abdom, weight & 39 & abdom, age, forearm, height, hip, neck, thigh, wrist & 4 \\
2 & abdom, wrist & 10 & abdom, age, chest, forearm, height, neck, thigh, wrist & 4 \\
3 & abdom, height & 10 & abdom, forearm, height, neck, wrist & 2 \\
4 & abdom, height, wrist & 9 & abdom, forearm, neck, weight, wrist & 2 \\
5 & abdom, weight, wrist & 8 & abdom, age, height, hip, thigh, wrist & 2 \\
6 & abdom, chest, height, wrist & 2 & abdom, age, height, hip, neck, thigh, wrist & 2 \\
7 & abdom, biceps, weight, wrist & 2 & abdom, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
8 & abdom, height, weight, wrist & 2 & abdom, age, biceps, chest, height, neck, wrist & 2 \\
9 & abdom, age, wrist & 2 & abdom, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
10 & abdom, age, height, neck, thigh, wrist & 2 & abdom, age, ankle, biceps, weight, wrist & 2 \\
%   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

@@

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
  \hline
original & projpred & 4.35 & 4.47 & 2 &   \\
& steplm & 4.38 & 4.47 & 7 &  \\
\hline
+ noisy features & projpred & 4.58 & 4.54 & 2 & 0  \\
& steplm & 5.89 & 5.43 & 19 & 13 \\
%   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two
  rows) and with extra noisy features (last two rows) estimated with
  10-fold cross-validation. Abbreviations: Full = full model; Selected =
  selected submodel; \# Selected = total number of features selected;
  \# Selected noisy = number of extra noisy features selected.}
\label{tab:model_performances}
\end{table}

@@

When the variable selection is repeated with different simulated data
sets, there is some variability in which variables are selected. We
measure the stability of variable selection by computing the entropy
of observed distribution over different models. The smallest entropy
would be obtained if the approach always selects the same set of
variables, and the largest entropy would be observed if the approach
would always select different set of variables.
Figure \ref{fig:entropy} reports the entropy scores for the different compared
methods. Lower entropy corresponds to a more stable
selection. Highly correlated predictive features may happen to be
alternately selected, making the measure of the stability of the
selection a non-trivial task. Entropy cannot distinguish the interchangeability 
due to correlation from instability. Thus, such a measure should be 
considerd as a relative and not as an absolute measure of stability.
The use of a reference model
improves slightly the stability of steplm in feature selection. The
projection predictive approach results to be far more stable than all
other approaches. This is likely due to projpred being based on better
decision theoretical formulation which 1) takes into account the full
predictive distribution and not just point estimate and 2) projects
the reference model posterior to the submodel instead of using a
simple refit of submodels.
